A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2018-07-26 paper/prab.tex
small changes
paper edits

\title{A Parallel General Purpose Multi-Objective Optimization Framework,
  with Application To Beam Dynamics}
%\thanks{A footnote to the article title}%

@@

The framework was then applied to a larger and untested beam dynamics problem at the AWA.
Optimization of the 3D beam size and energy spread was accomplished.
A scan of time step and hyper parameters was done to determine computational settings.
Then a full scale physics optimization was performed.
The resulting beam tune can and will be used in future TBA experiments at the AWA.
This problem also took advantage of the frameworks massively parallel capabilities by
running on 2624 processes on Bebop at LCRC.

>>>>

\title{A Parallel General Purpose Multi-Objective Optimization Framework,
  with Application To Electron Beam Dynamics}
%\thanks{A footnote to the article title}%

@@

The framework was then applied to a larger beam dynamics problem at the AWA.
Optimization of the 3D beam size and energy spread was accomplished.
A scan of time step and hyper parameters was done to determine computational settings.
Then a full scale physics optimization was performed.
The resulting beam tune can and will be used in future TBA experiments at the AWA.
This problem also took advantage of the frameworks massively parallel capabilities by
running on 2624 processes on Bebop at LCRC.
